EDA

### 2023-04-06 notebook/analysis-local.qmd
Create targets for models + preliminary results

---
title: "Issue area"
---

@@

```{r generate-preds}
preds <- m_full_ordbeta |> 
  predicted_draws(datagrid(model = m_full_ordbeta, work_field_code1 = unique), 
                  ndraws = 1000)

epreds <- m_full_ordbeta |> 
  epred_draws(datagrid(model = m_full_ordbeta, work_field_code1 = unique), 
              ndraws = 1000)
```

```{r plot-epred-issue}
epreds |> 
  ungroup() |> 
  mutate(work_field_code1 = fct_reorder(work_field_code1, .epred)) |> 
  ggplot(aes(x = .epred, y = work_field_code1)) +
  stat_halfeye(fill = clrs[5]) +
  scale_x_continuous(labels = label_percent(),
                     sec.axis = sec_axis(trans = ~ prop_to_provinces(.),
                                         name = "Expected provinces",
                                         breaks = seq(8, 32, 4))) +
  guides(fill = "none") +
  labs(x = "Expected proportion of provinces", y = NULL) +
  theme_ongo() +
  theme(axis.ticks.x.top = element_line(linewidth = 0.25, color = "grey50"))
```

>>>>

---
title: "Local connections"
---

@@

```{r generate-preds}
preds <- m_full_ordbeta |> 
  predicted_draws(datagrid(model = m_full_ordbeta, local_connect = unique), 
                  ndraws = 1000)

epreds <- m_full_ordbeta |> 
  epred_draws(datagrid(model = m_full_ordbeta, local_connect = unique), 
              ndraws = 1000)
```

```{r plot-epred-local}
epreds |> 
  ungroup() |> 
  mutate(local_connect = factor(local_connect, labels = c("No local connections", "Local connections"))) |> 
  ggplot(aes(x = .epred, y = local_connect)) +
  stat_halfeye(fill = clrs[2]) +
  scale_x_continuous(labels = label_percent(),
                     sec.axis = sec_axis(trans = ~ prop_to_provinces(.),
                                         name = "Expected provinces",
                                         breaks = seq(8, 32, 4))) +
  guides(fill = "none") +
  labs(x = "Expected proportion of provinces", y = NULL) +
  theme_ongo() +
  theme(axis.ticks.x.top = element_line(linewidth = 0.25, color = "grey50"))
```

### 2023-04-06 notebook/analysis-timing.qmd
Create targets for models + preliminary results

---
title: "Local connections"
---

@@

```{r generate-preds}
preds <- m_full_ordbeta |> 
  predicted_draws(datagrid(model = m_full_ordbeta, local_connect = unique), 
                  ndraws = 1000)

epreds <- m_full_ordbeta |> 
  epred_draws(datagrid(model = m_full_ordbeta, local_connect = unique), 
              ndraws = 1000)
```

```{r plot-epred-local}
epreds |> 
  ungroup() |> 
  mutate(local_connect = factor(local_connect, labels = c("No local connections", "Local connections"))) |> 
  ggplot(aes(x = .epred, y = local_connect)) +
  stat_halfeye(fill = clrs[2]) +
  scale_x_continuous(labels = label_percent(),
                     sec.axis = sec_axis(trans = ~ prop_to_provinces(.),
                                         name = "Expected provinces",
                                         breaks = seq(8, 32, 4))) +
  guides(fill = "none") +
  labs(x = "Expected proportion of provinces", y = NULL) +
  theme_ongo() +
  theme(axis.ticks.x.top = element_line(linewidth = 0.25, color = "grey50"))
```

>>>>

---
title: "Registration timing"
---

@@

```{r generate-preds}
preds <- m_full_ordbeta |> 
  predicted_draws(datagrid(model = m_full_ordbeta, years_since_law = 0:5), 
                  ndraws = 1000)

epreds <- m_full_ordbeta |> 
  epred_draws(datagrid(model = m_full_ordbeta, years_since_law = 0:5), 
              ndraws = 1000)
```

```{r plot-epred-timing}
epreds |> 
  mutate(years_since_law = factor(years_since_law)) |> 
  ggplot(aes(x = .epred, y = years_since_law)) +
  stat_halfeye(fill = clrs[7]) +
  scale_x_continuous(labels = label_percent(),
                     sec.axis = sec_axis(trans = ~ prop_to_provinces(.),
                                         name = "Expected provinces",
                                         breaks = seq(8, 32, 4))) +
  guides(fill = "none") +
  labs(x = "Expected proportion of provinces", y = "Years since law took effect in 2017") +
  theme_ongo() +
  theme(axis.ticks.x.top = element_line(linewidth = 0.25, color = "grey50"))
```

### 2023-04-06 notebook/exploratory.qmd
Create targets for models + preliminary results

# Map!

```{r load-packages-data, message=FALSE, warning=FALSE}
library(tidyverse)
library(targets)
library(here)
library(sf)

@@

# Load targets
mapdata <- tar_read(ongo_mapdata)
```

```{r ongo-map, fig.height=6, fig.width=8, message=FALSE, warning=FALSE}
labeldata <- mapdata |> 
  filter(ro_count > 0)

plot_map <- ggplot() +
  geom_sf(data = mapdata,
          aes(fill = ro_count), color = "white") +
  scale_fill_viridis_c(option = "mako", begin = 0.1, end = 0.9, direction = -1) +
  geom_sf_label(data = labeldata, aes(label = ro_count), 
                nudge_y = -0.8 , nudge_x = -0.1, size = 3, alpha = 0.7) +
  theme_void()
plot_map
```

>>>>

```{r load-packages-data, message=FALSE, warning=FALSE}
library(tidyverse)
library(targets)
library(here)
library(sf)
library(ggrepel)

@@

# Load targets
mapdata <- tar_read(ongo_mapdata)
invisible(list2env(tar_read(graphic_functions), .GlobalEnv))
set_annotation_fonts()
```

# Timeline of registration

TODO

# Distribution of outcome

TODO

# Map of provinces and counts

```{r ongo-map, fig.height=5, fig.width=7, message=FALSE, warning=FALSE}
# Use aes(geometry) and stat = "sf_coordinates" to make geom_label_repel() work
# with geom_sf(): https://github.com/slowkow/ggrepel/issues/111#issuecomment-416853013
labeldata <- mapdata |> 
  filter(ro_count > 0)

plot_map <- ggplot() +
  geom_sf(data = mapdata,
          aes(fill = ro_count), color = "white") +
  scale_fill_viridis_c(option = "mako", begin = 0.1, end = 0.9, direction = -1,
                       guide = "none") +
  geom_label_repel(data = labeldata, 
                   aes(label = ro_count, geometry = geometry),
                   stat = "sf_coordinates",
                   size = 3) +
  theme_void()
plot_map
```
